raptr: Representative and Adequate Prioritization Toolkit in R

### 2017-08-22 code/rmarkdown/article.Rmd
update doi

# Data accessibility
The \texttt{raptr R} package can be downloaded from The Comprehensive R Archive Network (\url{https://CRAN.R-project.org/package=raptr}). To permit replication and validation of this study, all data, code, and results are stored in an online repository (\url{https://github.com/jeffreyhanson/raptr-manuscript}) and are available at the DOI: \texttt{10.5281/zenodo.823768}.

>>>>

# Data accessibility
The \texttt{raptr R} package can be downloaded from The Comprehensive R Archive Network (\url{https://CRAN.R-project.org/package=raptr}). To permit replication and validation of this study, all data, code, and results are stored in an online repository (\url{https://github.com/jeffreyhanson/raptr-manuscript}) and are available at the DOI: \texttt{10.5281/zenodo.846477}.
